% Adapted from https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Nicholas Williams}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titleformat{\subsubsection}{\sffamily\footnotesize}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {biostatistics, causal inference, R programming},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{\myname}

    % contact info
    \vspace{1em}
    \begin{minipage}[t]{0.64\textwidth}
        Department of Epidemiology \\
        Mailman School of Public Health, Columbia University
        \\ New York, New York, USA
    \end{minipage}
    \begin{minipage}[t]{0.34\textwidth}
        e: \href{mailto:ntw2117@cumc.columbia.edu}{ntw2117@cumc.columbia.edu} \\
        p: +1 719 650 1307 \\
        w: \href{https://nicholastwilliams.com/}{nicholastwilliams.com}
    \end{minipage}
    \vspace{0.5em}

    \section*{Education}

    \begin{tablist}
    
    	\item[Ph.D.] \tab Ongoing \tab Biostatistics, University of California, Berkeley

        \item[M.P.H.]  \tab 2019 \tab Biostatistics, Columbia University

        \item[B.A.]  \tab 2017 \tab Psychology, University of Colorado at Boulder

    \end{tablist}

    \section*{Professional}
    
    \subsection*{Academic}

    \begin{tablist}
    
    	\item[2021-] \tab Columbia University, Mailman School of Public Health \\
						  Senior Data Analyst III \\
						  Department of Epidemiology

        \item[2019-21] \tab Weill Cornell Medical College \\
                            Research Biostatistician I  \\
                            Division of Biostatistics, Department of Population Health Sciences 
        
        \item[2018]  \tab Columbia University, Mailman School of Public Health \\
                          Research Assistant for Christine Mauro, Ph.D. \\
                          Department of Biostatistics

    \end{tablist}
    
    \subsection*{Consulting}
    
    \begin{tablist}
    
	\item[2025-] \tab TLRevolution, Independent Consultant
						  
	\item[2021] \tab Bayer AG, Independent Consultant
    
    \end{tablist}

    \section*{Research Interests}

    \begin{itemize}

        \item Nonparametric causal inference.

        \item Research software engineering.

    \end{itemize}

    \section*{Publications}
    
    \subsection*{Research in statistics}
    
    \begin{tablist}
   
    \item[2025] \tab \textbf{Williams, N.}, Liu, R., Hoffman, K., Forrest, S., Rudolph, K. and Díaz, I. \enquote{Two-stage targeted minimum-loss based estimation for non-negative two-part outcomes.} \textit{Statistical Methods in Medical Research}. DOI: 10.1177/09622802251340245
    
    \item[2025] \tab Díaz, I., \textbf{Williams, N.}, Hoffman, K. L. and Hejazi, N. S. \enquote{Author correction to: `Causal survival analysis under competing risks using longitudinal modified treatment policies.'} \textit{Lifetime Data Analysis}.
    
    \item[2025] \tab Rudolph, K. E., \textbf{Williams, N. T.}, Stuart, E. A. and Díaz, I. \enquote{Improving efficiency in transporting average treatment effects.} \textit{Biometrika}.
    
    \item[2024] \tab Rudolph, K. E., \textbf{Williams, N. T.} and Díaz, I. \enquote{Practical causal mediation analysis: Extending nonparametric estimators to accommodate multiple mediators and multiple intermediate confounders.} \textit{Biostatistics}.
    
    \item[2024] \tab Rudolph, K. E., \textbf{Williams, N.} and Díaz, I. \enquote{Using instrumental variables to address unmeasured confounding in causal mediation analysis.} \textit{Biometrics}.
    
    \item[2023] \tab Díaz, I., \textbf{Williams, N.} and Rudolph, K. E. \enquote{Efficient and flexible mediation analysis with time-varying mediators, treatments, and confounders.} \textit{Journal of Causal Inference}.
    
    \item[2023] \tab Rudolph, K. E., \textbf{Williams, N. T.}, Miles, C. H., Antonelli, J. and Díaz, I. \enquote{All models are wrong, but which are useful? Comparing parametric and nonparametric estimation of causal effects in finite samples.} \textit{Journal of Causal Inference}.
    
    \item[2023] \tab Rudolph, K. E., \textbf{Williams, N.} and Díaz, I. \enquote{Efficient and flexible estimation of natural direct and indirect effects under intermediate confounding and monotonicity constraints.} \textit{Biometrics}.
    
        \item[2022] \tab \textbf{Williams, N.}, Rosenblum, M. and Díaz, I. \enquote {Optimizing Precision and Power by Machine Learning in Randomized Trials, with an Application to COVID-19.} \textit{Journal of the Royal Statistical Society: Series A}. DOI: \href{https://doi.org/10.1111/rssa.12915}{10.1111/rssa.12915}
    
       \item[2021] \tab Díaz, I., \textbf{Williams, N.}, Hoffman, K. and Schenck, E. \enquote{Non-parametric causal effects based on longitudinal modified treatment policies.} \textit{Journal of the American Statistical Association - Theory and Methods}. DOI: \href{https://doi.org/10.1080/01621459.2021.1955691}{10.1080/01621459.2021.1955691}
       
    \end{tablist}

    \subsection*{Applied Epidemiology}

    \begin{tablist}
    
    \item[2025] \tab Rudolph, K.E., Inose, S., \textbf{Williams, N.T.}, Hoffman, K.L., Forrest, S.E., Ross, R.K., Milazzo, F., Diaz, I., Doan, L., Samples, H., Olfson, M., Crystal, S., Cerda, M. and Gao, Y.N. \enquote{Mediation of chronic pain and disability on opioid use disorder risk by pain management practices among adult Medicaid patients, 2016-2019.} \textit{American Journal of Epidemiology}.
    
    \item[2025] \tab Perry, A., Krawczyk, N., Samples, H., Martins, S.S., Hoffman, K., \textbf{Williams, N.T.}, Hung, A., Ross, R., Doan, L., Rudolph, K.E. and Cerda, M. \enquote{Opioid Dose, duration, and risk of use disorder in Medicaid patients with musculoskeletal pain.} \textit{Pain Medicine}. DOI: \href{https://doi.org/10.1093/pm/pnaf077}{10.1093/pm/pnaf077} 
    
    \item[2024] \tab Rudolph, K. E., \textbf{Williams, N. T.}, Díaz, I., Forrest, S., Hoffman, K. L., Samples, H., Olfson, M., Doan, L., Cerdá, M. and Ross, R. K. \enquote{Pain management treatments and opioid use disorder risk in Medicaid patients.} \textit{American Journal of Preventive Medicine}.
    
    \item[2024] \tab Hoffman, K. L., Milazzo, F., \textbf{Williams, N. T.}, Samples, H., Olfson, M., Díaz, I., Doan, L., Cerdá, M., Crystal, S. and Rudolph, K. E. \enquote{Independent and joint contributions of physical disability and chronic pain to incident opioid use disorder and opioid overdose among Medicaid patients.} \textit{Psychological Medicine}.
    
        \item[2023] \tab Rudolph, K.E., \textbf{Williams, N.}, Díaz, I., Luo, S.X., Rotrosen, J. and Nunes, E.V. \enquote{Optimally choosing medication type for patients with opioid use disorder.} \textit{American Journal of Epidemiology}. DOI: \href{https://doi.org/10.1093/aje/kwac217}{10.1093/aje/kwac217}
        
        \item[2023] \tab Rudolph, K. E., \textbf{Williams, N. T.}, Milazzo, F., Venkataramani, A. and O’Brien, R. \enquote{Has the opening of Amazon fulfillment centers affected demand for disability insurance?} \textit{PLOS ONE}.
        
        \item[2022] \tab Rudolph, K. E., \textbf{Williams, N. T.}, Goodwin, A. T. S., Shulman, M., Fishman, M., Díaz, I., Luo, S., Rotrosen, J. and Nunes, E. V. \enquote{Buprenorphine \& methadone dosing strategies to reduce risk of relapse in the treatment of opioid use disorder.} \textit{Drug and Alcohol Dependence}.
        
            	\item[2022]\tab Hoffman, K.L., Schenck, E.J., Satlin, M.J., Whalen, W., Pan, D., \textbf{Williams, N.} and Díaz, I. \enquote{Comparison of a target trial emulation framework vs Cox regression to estimate the association of corticosteroids with COVID-19 mortality.} \textit{JAMA Network Open}. DOI: 10.1001/jamanetworkopen.2022.34425

    \item[2022] \tab Min. J.Y., Simmons, W., Banerjee, S., Wang, F., \textbf{Williams, N.}, Zhang, Y., Reese, A.B., Mushlin, A.I. and Flory, J.H. \enquote{Association between antidiabetic drug use and the risk of COVID-19 hospitalization in the INSIGHT Clinical Research Network in New York City.} \textit{Diabetes, Obesity and Metabolism}. DOI: 10.1111/dom.14704
    
    \item[2022] \tab Min, J.Y., \textbf{Williams, N.}, Simmons, W., Banerjee, S., Wang, F., Zhang, Y., Reese, A.B., Mushlin, A.I. and Flory, J.H. \enquote{Baselin Haemoglobin A1c and the Risk of COVID-19 Hospitalization Among Patients with Diabetes in the INSIGHT Clinical Research Network.} \textit{Diabetic Medicine}. DOI: 10.1111/dme.14815 
    
    \item[2022] \tab Hoffman, J.W., Bitar, R.C., \textbf{Williams, N.}, Steineman, B.D., Sturnick, D.R., Garrison, G.W., Demetracopoulos, C.A., Drakos, M.C. and O'Malley, M.J. \enquote{Orthosis and foot structure affect the fifth metatarsal principal strains during simulated level walking.} \textit{The American Journal of Sports Medicine}. DOI: \href{https://doi.org/10.1177/03635465221079652}{10.1177/03635465221079652}
    
    \item[2022] \tab Punjani, N., Alawamlh, O.H., Kim, S.J., Salter, C.A., Wald, G., Feliciano, M., \textbf{Williams, N.}, Dudley, V., and Goldstein, M. \enquote{Changes in semen analysis over time: A temporal trend analysis of 20 years of subfertile non-azoospermic men.} \textit{World Journal of Mens Health}. DOI: \href{https://doi.org/10.5534/wjmh.210201}{10.5534/wjmh.210201}
    
     \item[2021] \tab Winston, G., Guadix, S., Lavieri, M., Uribe-Cardenas, R., Kocharian, G., \textbf{Williams, N.}, Sholle, E., Grinspan, Z., and Hoffman, C. \enquote{Closed-Loop Vagal Nerve Stimulation for Intractable Epilepsy: A Single-Center Experience.} \textit{Seizure: European Journal of Epilepsy}. DOI: \href{https://doi.org/10.1016/j.seizure.2021.03.030}{10.1016/j.seizure.2021.03.030}
    
    \item[2021] \tab Goel, A.R., Bruce, H.A, \textbf{Williams, N.} and Alexiades, G. \enquote{Long-Term Effects of Hearing Aids on Hearing Ability in Patients with Sensorineural Hearing Loss.} \textit{Journal of the American Academy of Audiology}.
    
    \item[2020] \tab Thiesmeyer, J.W., Ullmann, T.M., Greenberg, J., \textbf{Williams, N.T.}, Limberg, J., Stefanova, D., Beninato, T., Finnerty, B.M., Vignaud, T., Leclerc, J., Fahey III, T.J., Mirallie, E.M., Brunaud, L. and Zarnegar, R..\enquote{Hypertension resolution after adrenalectomy for primary hyperaldosteronism: Which is the best predictive model?} \textit{Surgery}. DOI: \href{https://doi.org/10.1016/j.surg.2020.04.017}{10.1016/j.surg.2020.04.017}  
	
	\item[2020] \tab Riley, C.A., Zheng, Z., \textbf{Williams, N.}, Smith, T.L., Orlandi, R.R. and Tabaee, A. \enquote{Concordance of self‐reported practice patterns of American Rhinologic Society members with the International Consensus Statement of Allergy and Rhinology: Rhinosinusitis} \textit{International Forum of Allergy and Rhinology}. DOI: \href{https://doi.org/10.1002/alr.22533}{10.1002/alr.22533} 
	
	\item[2020] \tab Day, J., Conti, M.S., \textbf{Williams, N.}, Ellis, S.J., Deland, J.T. and Cody, E.A. \enquote{Contribution of First-Tarsometatarsal Joint Fusion to Deformity Correction in the Treatment of Adult-Acquired Flatfoot Deformity.} \textit{Foot and Ankle Orthopaedics}. DOI: \href{https://doi.org/10.1177/2473011420927321}{10.1177/2473011420927321}
	
	\item[2020] \tab Day, J., Kim, J., Conti, M.S., \textbf{Williams, N.}, Deland, J.T. and Ellis, S.J. \enquote{Outcomes of Idiopathic Flexible Flatfoot Deformity Reconstruction in the Young Patient.} \textit{Foot and Ankle Orthopaedics}. DOI: \href{https://doi.org/10.1177/2473011420937985}{10.1177/2473011420937985}
	
	\item[2020] \tab Cronin, S., Conti, M., \textbf{Williams, N.} and Ellis., S.J. \enquote{Relationship Between Demographic and Radiographic Characteristics and Second Ray Pathology in Hallux Valgus Patients.} \textit{Foot and Ankle Orthopaedics}. DOI: \href{https://doi.org/10.1177/2473011420909088}{https://doi.org/10.1177/2473011420909088}

	\item[2019] \tab Hussain, I., Winston, G.M., Goldberg, J., Curri, C., \textbf{Williams, N.}, Chazen, J.L., Greenfield, J.P. and Baaj, A.A. \enquote{Impact of imaging modality, age, and gender on craniocervical junction angles in adults without structural pathology.} \textit{Journal of Craniovertebral Junction and Spine}. PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32089618}{32089618}

    \end{tablist}
    
    \subsection*{Software}
    
    \begin{tablist}
    
    \item[2024] \tab \textbf{Williams, N.} and Rudolph, K. E. \enquote{A drug classification pipeline for Medicaid claims using RxNorm.} \textit{arXiv preprint arXiv:2404.01514}.
    
    \item[2023] \tab \textbf{Williams, N.} and Díaz, I. \enquote{lmtp: An R package for estimating the causal effects of modified treatment policies.} \textit{Observational Studies}, 9(2): 103--122.
    
    \end{tablist}
    
    \subsection*{Commentaries}
    
    \begin{tablist}
    
       \item[2025] \tab \textbf{Williams, N.}, Hung, A. and Rudolph K. \enquote{Re: Don’t Let Your Analysis Go to Seed: On the Impact of Random Seed on Machine Learning-based Causal Inference.} \textit{Epidemiology}. DOI: 10.1097/EDE.0000000000001860
   
   	\item[2025]\tab \textbf{Williams, N.}, Rudolph, K.E. and Díaz, I. \enquote{Comment on `Do we need flexible machine-learning algorithms to assess the effect of long-term exposure to fine particulate matter on mortality?'.} \textit{Environmental Epidemiology}. DOI: 10.1097/EE9.0000000000000407
    
    \end{tablist}
    
    \subsection*{Preprints and manuscripts under review}
    
    \begin{tablist}
    
     \item[2025] \tab \textbf{Williams, N.}, Rudolph, K. and Díaz, I. \enquote{Nonparametric estimation of an optimal treatment rule with fused randomized trials and missing effect modifiers.} \textit{arXiv preprint 2506.10863}.
    
    \item[2024] \tab Liu, R., \textbf{Williams, N. T.}, Rudolph, K. E. and Díaz, I. \enquote{General targeted machine learning for modern causal mediation analysis.} \textit{arXiv preprint arXiv:2408.14620}.
    
    \item[2024] \tab Susmann, H., \textbf{Williams, N. T.}, Rudolph, K. E. and Díaz, I. \enquote{Longitudinal generalizations of the average treatment effect on the treated for multi-valued and continuous treatments.} \textit{arXiv preprint arXiv:2405.06135}.
    
    \item[2024] \tab Vo, T.-T., \textbf{Williams, N.}, Liu, R., Rudolph, K. E. and Díaz, I. \enquote{Recanting twins: Addressing intermediate confounding in mediation analysis.} \textit{arXiv preprint arXiv:2401.04450}.
    
    \item[2024] \tab Gilbert, B., Hoffman, K. L., \textbf{Williams, N.}, Rudolph, K. E., Schenck, E. J. and Díaz, I. \enquote{Identification and estimation of mediational effects of longitudinal modified treatment policies.} \textit{arXiv preprint arXiv:2403.09928}.

    
    \end{tablist}
    
    \section*{Software}
    
    \subsection*{Maintainer}
    
    \begin{tablist}
    
    	\item[{\footnotesize \texttt{lmtp}}] \tab \texttt{R}: Non-Parametric Causal Effects of Feasible Interventions Based on Modified Treatment Policies
	
	    	\item[{\footnotesize \texttt{crumble}}] \tab \texttt{R}: Mediation Analysis Using Modified Treatment Policies, Recanting Twins, and Riesz Representers
		
		\item[{\footnotesize \texttt{mlr3superlearner}}] \tab \texttt{R}: Super learner fitting and prediction using mlr3
		
		\item[{\footnotesize \texttt{adjrct}}] \tab \texttt{R}: Doubly-Robust and Efficient Estimators for Survival and Ordinal Outcomes in RCTs Without Proportional Hazards or Odds Assumptions
    
    \end{tablist}
    
    \subsection*{Contributer}
    
    \begin{tablist}
    
    	\item[{\footnotesize \texttt{broom}}] \tab \texttt{R}: Convert Statistical Objects into Tidy Tibbles
    
    \end{tablist}

    \section*{Conference Activity}
    
    \subsection*{Short courses}
    
     \enquote{Beyond the ATE.} Materials available at \href{https://beyondtheate.com/}{beyondtheate.com}.\\
    
    \begin{itemize}
    
    \item \hspace{1em} 2025 \textit{Society for Epidemiology Research}, Boston, MA. 
    \item \hspace{1em} 2025 \textit{Lifetime Data Science}, Brooklyn, NY. 
    \item \hspace{1em} 2025 \textit{American Causal Inference Conference}, Detroit, MI. 
    \item \hspace{1em} 2024 \textit{Society for Epidemiology Research}, Austin, TX. 
    
    \end{itemize}
    
    \enquote{Modern Causal Mediation Analysis.} 
    
    \begin{itemize}
    
        \item \hspace{1em} 2025 \textit{Society for Epidemiology Research}, Boston, MA. 
    
    \end{itemize}

    \subsection*{Conference Presentations}
    % Asterisk* indicates paper published in \enquote{Peer-Reviewed Proceedings} above.
    
    \subsubsection{Talks}
    
    \begin{tablist}
    
    \item[2025] \tab \textbf{Williams, N.T.}, Rudolph, K.E., and Díaz, I. \enquote{Nonparametric estimation of the optimal dynamic treatment rule in fused randomized trials with a missing effect modifier.} \textit{American Causal Inference Conference}, Detroit, MI.
    
    \end{tablist}
    
    \subsubsection{Posters}

    \begin{tablist}
    
    \item[2024] \tab \textbf{Williams, N.T.}, Liu, R., Hoffman, K.E., Forrest, S., Rudolph, K.E., and Díaz, I. \enquote{Two-step targeted minimum-loss based estimation for non-negative two-part outcomes.} \textit{American Causal Inference Conference}, Seattle, WA.

    \end{tablist}
    
    \section*{Service}
    
    \subsection*{Academic Journal Peer Review}
    
    \begin{itemize}
    
    	\item \textit{The R Journal}
    
    \end{itemize}

    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}

        \item[2017] \tab Graduate with Distinction, University of Colorado at Boulder

    \end{tablist}

    \subsection*{Grants and Fellowships}

    \begin{tablist}

        \item[2015] \tab Virginia Summer Undergraduate Research Initiative. Project: \enquote{The relationship between cognitively oriented verbs and affect.}

    \end{tablist}

    \section*{Teaching}
    
    \subsection*{Weill Cornell Medicine}
    
    \begin{itemize}
    
    	\item Data Science I -- Teaching Assistant
    
    \end{itemize}

    \subsection*{Columbia University}
    
    \begin{itemize}
    	
    	\item Categorical Data Analysis -- Lead Teaching Assistant
    	\item Research Methods, Quantitative Foundations -- Teaching Assistant
    
    \end{itemize}

    \section*{Professional Affiliations}

    \begin{tablist}

        \item[2020--] \tab American Statistical Association
        
        	\item[2023--] \tab American Mountain Guides Association -- Certified Single Pitch Instructor

    \end{tablist}

    \section*{Technical Skills}

    \begin{itemize}

        \item \texttt{R} \tab expert
        
        \item \texttt{Julia} \tab intermediate
        
        	\item \texttt{SAS}

		\item \texttt{SQL}
        
        \item \texttt{C++} \tab novice
        
        \item \texttt{Ruby}

    \end{itemize}

    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        %\vspace{6em}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
